Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
tassage
+ citation Laure

\usepackage{dcolumn}

@@

\begin{figure}
\begin{center}
\includegraphics{figures/gopan_reps}
\end{center}
\caption{The invariant for Prog.~\ref{lst:gopan_reps}: the piecewise linear, solid line is the strongest invariant, the grayed polyhedron is its convex hull.}
\label{fig:gopan_reps_invariant} 
\end{figure}

@@

In order to find focus paths, we solve an SMT formula which is satisfiable when
there exist a path starting at a point $p_i \in P_R$ in a state included in the
current invariant candidate $X_i$, and arriving at a point $p_j \in P_R$ in a
state outside $X_j$. In this case, we construct this path using the model and
update $X_j$. When $p_i = p_j$, meaning that the path is actually a self-loop,
we can apply a widening/narrowing sequence, or even compute the transitive
closure of the loop using abstract acceleration. % TODO citation laure gonnord

@@

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible:
\begin{itemize}
\item \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics.
\item Replacing the results of nonlinear operations by ``unknown''.
\end{itemize}
However, such transformations are not yet implemented in our tool.
% TODO: c'est si dur de remplacer * non lineaire par undef?

>>>>

\usepackage{enumitem}
\usepackage{dcolumn}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.75]{figures/gopan_reps}
\end{center}
\caption{The invariant for Prog.~\ref{lst:gopan_reps}: the piecewise linear, solid line is the strongest invariant, the grayed polyhedron is its convex hull.}
\label{fig:gopan_reps_invariant} 
\end{figure}

@@

In order to find focus paths, we solve an SMT formula which is satisfiable when
there exist a path starting at a point $p_i \in P_R$ in a state included in the
current invariant candidate $X_i$, and arriving at a point $p_j \in P_R$ in a
state outside $X_j$. In this case, we construct this path using the model and
update $X_j$. When $p_i = p_j$, meaning that the path is actually a self-loop,
we can apply a widening/narrowing sequence, or even compute the transitive
closure of the loop (or an approximation thereof, or its application to $X_i$)
using abstract acceleration~\cite{DBLP:conf/sas/GonnordH06}.

@@

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible:
\begin{itemize}[itemsep=-\parsep,topsep=0pt,partopsep=0pt]
\item \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics.
\item Replacing the results of nonlinear operations by ``unknown''.
\end{itemize}
However, such transformations are not yet implemented in our tool.
% TODO: c'est si dur de remplacer * non lineaire par undef?
